---
title: "K-cluster "
Athur:"George Garcia"
date:"11/29/2021"
output:
  html_document:
    df_print: paged
---

---
```{r setup, include=FALSE}
library(knitr)
library(stats)
knitr::opts_chunk$set(echo = TRUE)
```

```{r global.options, include = FALSE}
knitr::opts_chunk$set(
    cache       = TRUE,     # if TRUE knitr will cache the results to reuse in future knits
    fig.align   = 'center', # how to align graphics in the final doc. 'left', 'right', 'center'
    fig.path    = 'figs/',  # file path to the directory where knitr shall store the graphics files
    #results     = 'asis',   # knitr will pass through results without reformatting them
    echo        = TRUE,     # in FALSE knitr will not display code in the code chunk above it's results
    message     = TRUE,     # if FALSE knitr will not display any messages generated by code
    strip.white = TRUE,     # if FALSE knitr will not remove white spaces at the beg or end of code chunk
    warning     = FALSE)    # if FALSE knitr will not display any warning messages in the final document
```


```{r}
WW_test <- read.csv("~/Downloads/Website Data Sets/white_wine_test")

WW_training <- read.csv("~/Downloads/Website Data Sets/white_wine_training")
```


**Q11  Input and standardize both the training and test data sets. **
```{r}
## Standardizing both data sets with scale() command##
##training
X <- subset(WW_training, select = c("alcohol", "sugar"))
Xs <- as.data.frame(scale(X))
colnames(Xs) <- c("alcohol_z", "sugar_z")
##test
T <- subset(WW_test, select = c("alcohol", "sugar"))
Ts <- as.data.frame(scale(T))
colnames(Ts) <- c("alcohol_z", "sugar_z")
```

**Q12 Run k‐means clustering on the training data set, using two clusters.**
```{r}
#kmeans() command for 2 clusters 
kmeans01 <- kmeans(Xs, centers = 2)
cluster <- as.factor(kmeans01$cluster)
```

**Q13  Give the mean of each variable within each cluster and use the means to identify a “Dry wines” and a “Sweet wines” cluster.**
```{r}
#disdplay the mean of the cluster 
Cluster1 <- Xs [ which(cluster == 1),]
Cluster2 <- Xs [ which(cluster == 2),]
summary(Cluster1)
summary(Cluster2)
```


**Q14 Validate the clustering results by running k‐means clustering on the test data set, using two clusters, and identifying a “Dry wines” and a “Sweet wines” cluster.**
```{r}
colnames(Ts) <- c("alcohol_z", "sugar_z")
kmeans01_test <- kmeans(Ts, centers = 2)
cluster_test <- as.factor(kmeans01_test$cluster)
Cluster1_test <- Ts[ which(cluster_test == 1), ]
Cluster2_test <- Ts[ which(cluster_test == 2), ]
summary(Cluster1_test); summary(Cluster2_test)
```